Garamszegi example

### 2021-04-09 garamszegi_example.rmd
not sure what changed, it works perfectly fine on a fresh computer

---
title: "Example"
author: "Michael Li and Ben Bolker"
output:
  pdf_document: default
  mathjax: default
  html_document: null
bibliography: phyloglmm.bib
urlcolor: blue
---

@@

Similarily, fitting using glmmTMB:

>>>>

---
title: "Garamszegi example"
author: "Michael Li and Ben Bolker"
output:
  pdf_document: default
  mathjax: default
  html_document: null
bibliography: phyloglmm.bib
urlcolor: blue
---

@@

Similarly, fitting using glmmTMB:
